---
title: "ggplot2"
author: "Henry Mendoza Rivera and Gloria Bautista"
date: "6/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Estableciendo formatos
```{r}
options(scipen=999)  # turn-off scientific notation like 1e+48
theme_get()
#theme_set(theme_bw())  # pre-set the bw theme.
```

## Cargando la base de datos: Software


```{r}

softwareESP<-read.csv("https://raw.githubusercontent.com/hmendozar17/R-Learning/master/Datasets/softwareESPdepurada.csv", header=TRUE,sep = ";")
## nrow(software) = 149 participants
```

## Cleaning database Software

```{r}
str(softwareESP)
softwareESP$TiempoEjec<-as.numeric(softwareESP$TiempoEjec)
str(softwareESP)
```

# instalacion de ggplot2
```{r}
install.packages("ggplot2")
library(ggplot2)
```

## Ayuda con ggplot2
```{r}
?ggplot2 # ayuda para ggplot2
```


```{r}
data(package = .packages(all.available = TRUE))# to list the data sets in all *available* packages.

data(package="ggplot2") # to list  the data stes in ggplot2 package
```
# Diagrama de barras 
## Visualizaci贸n de datos categ贸ricos

```{r}
g1<-ggplot(softwareESP, aes(x =a$GENERO))
g1
# without using ggplot 2
with(softwareESP, table(GENERO))
```


```{r}
#Hemerson code start
a<-softwareESP %>% group_by(GENERO) %>% summarize(mean(Nota))
a
colnames(a)<-c("Genero","Nota")

#Hemerson code end
g1<-ggplot(a, aes(x =a$GENERO,y=a$Nota))
g1
?geom_bar()       
g1+ geom_bar()+labs(title = "Distribuci贸n de los estudiantes por Genero")

```

# Visualizaci贸n de datos resumen (medias)
```{r}
# Very basic bar graph
ggplot(data=software, aes(x=time, y=total_bill)) +
    geom_bar(stat="identity")
```

data("mtcars")
mtcars
attach(mtcars)
names(mtcars)

# Boxplot
```{r}
p <- ggplot(softwareESP, aes(x =softwareESP$GENERO , y = softwareESP$TiempoEjec)) + 
  geom_boxplot() +
  theme_bluewhite()
p
```


# Diagrama de dispersion
```{r}
Nota.TiempoEjec <- ggplot(softwareESP, aes(softwareESP$Nota, softwareESP$TiempoEjec)) +
  geom_point() 
Nota.TiempoEjec


```


# Kernel density plots for mpg
# grouped by number of gears (indicated by color)

qqplot(mpg, data=mtcars, geom="density", fill=gear, alpha=I(.5),main="Distribution of Gas Milage", xlab="Miles Per Gallon",ylab="Density")



# Scatterplot of mpg vs. hp for each combination of gears and cylinders
# in each facet, transmittion type is represented by shape and color
qplot(hp, mpg, data=mtcars, shape=am, color=am, 
      facets=gear~cyl, size=I(3),
      xlab="Horsepower", ylab="Miles per Gallon") 

# Separate regressions of mpg on weight for each number of cylinders
qplot(wt, mpg, data=mtcars, geom=c("point", "smooth"), 
      method="lm", formula=y~x, color=cyl, 
      main="Regression of MPG on Weight", 
      xlab="Weight", ylab="Miles per Gallon")

# Boxplots of mpg by number of gears 
# observations (points) are overlayed and jittered
qplot(gear, mpg, data=mtcars, geom=c("boxplot", "jitter"), 
      fill=gear, main="Mileage by Gear Number",
      xlab="", ylab="Miles per Gallon")

------------------------------------------------------
  GGplot for more than 2 graphics
--------------------------------------------
  
  install.packages("ggplot")
  library(ggplot2)

# This example uses the ChickWeight dataset, which comes with ggplot2
# First plot
p1 <- 
  ggplot(ChickWeight, aes(x=Time, y=weight, colour=Diet, group=Chick)) +
  geom_line() +
  ggtitle("Growth curve for individual chicks")

# Second plot
p2 <- 
  ggplot(ChickWeight, aes(x=Time, y=weight, colour=Diet)) +
  geom_point(alpha=.3) +
  geom_smooth(alpha=.2, size=1) +
  ggtitle("Fitted growth curve per diet")

# Third plot
p3 <- 
  ggplot(subset(ChickWeight, Time==21), aes(x=weight, colour=Diet)) +
  geom_density() +
  ggtitle("Final weight, by diet")

# Fourth plot
p4 <- 
  ggplot(subset(ChickWeight, Time==21), aes(x=weight, fill=Diet)) +
  geom_histogram(colour="black", binwidth=50) +
  facet_grid(Diet ~ .) +
  ggtitle("Final weight, by diet") +
  theme(legend.position="none")        # No legend (redundant in this graph)    





#### using categorical variable

fit <- glm(wealth_indicator ~  factor(ranking) + age_in_years + factor(ranking) * age_in_years)

References
http://www.cookbook-r.com/Graphs/Bar_and_line_graphs_(ggplot2)/


# create factors with value labels 

gear <- factor(gear,levels=c(3,4,5),labels=c("3gears","4gears","5gears")) 

am <- factor(am,levels=c(0,1), labels=c("Automatic","Manual")) 

cyl <- factor(cyl,levels=c(4,6,8),labels=c("4cyl","6cyl","8cyl")) 









